Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-31 fmics/paper.tex
Reword paragraph before Theorem 3

We formulate the difference between the $\mathsf{RS}$ values and their corresponding $\mathsf{true\_sum}$s, caused by the delay, as $\mathsf{error}$.
To meet the tolerance acceptable for quench prevention, the specification of SRS requires a bound on the value of this $\mathsf{error}$.
Considering any possible input stream to SRS, such a bound on the $\mathsf{error}$ value will be infinite.
However, according to extensive experimental analysis, the beam loss over time follows some patterns.
Thus, formulating some characterization of the input stream to SRS structure as constraints on $D$, will help defining a tighter bound on the $\mathsf{error}$.
One of these constraints is a maximum value on the difference between two consecutive count values.
This value can be inferred from the highest quench level thresholds.

>>>>

We formulate the difference between the $\mathsf{RS}$ values and their corresponding $\mathsf{true\_sum}$s, caused by the delay, as $\mathsf{error}$.
To meet the tolerance acceptable for quench prevention, the SRS specification requires a bound on this $\mathsf{error}$.
Without restricting the input stream, the $\mathsf{error}$ is unbounded\footnote{For any bound, we can construct an input stream that causes the bound to be exceeded by, for example, having a sequence of zeroes followed by a sequence of count values much higher than the bound.}.
However, according to extensive experimental analysis, the beam loss over time follows some patterns.
By formulating some characterization of the input stream as constraints on $D$, we can recover a bound on the $\mathsf{error}$.
One of these constraints is a maximum value for the difference between two consecutive count values.
This ``maximum jump size'' can be inferred from the highest quench level thresholds.
